---
title: "SeattleWorkingFile1819v2"
author: "CHENG Xin Yuan"
date: "16 March 2019"
output: word_document
---

```{r}
# packages <- c('maptools','spatstat','mapsapi','tmap','tmaptools','osrm','devtools','rgdal','osmdata','sf','sp','spdep','tidyverse')

packages <- c('osrm','tmaptools','osmdata','rgdal','maptools','raster','spatstat','sf','sp','tmap','tidyverse')

for (p in packages) {
  if(!require(p, character.only = T)) {
    install.packages(p)
  }
  library(p, character.only = T)
}
```

***
# Deriving the distances between the Attractions (10 in Downtown, 1 Space Needle) and every Downtown Airbnb listing
## Workings to derive the Airbnb Listings for DownTown Seattle
```{r}
#now we want to add the class description
zones = st_read(dsn = "data/spatial", layer = "Zoning_Generalized")
st_crs(zones) #uses CRS espg 4326 (WGS84)

#transform to EPSG:32148 NAD83
zones_32148 <- st_transform(zones, 32148)
st_crs(zones_32148)

#creating projection object and checking that it is correct
crs_object <- st_crs(zones_32148) 
class(crs_object)
list(crs_object)
```

```{r}
#transforming listings as sf data
#ALWAYS LONG THEN LAT
listings = read_csv("data/aspatial/listings.csv")
listings_sf <- st_as_sf(listings, 
                       coords = c("longitude", "latitude"), crs = 4326)
listings_32148 <- st_transform(listings_sf, crs_object)
st_crs(listings_32148)
st_bbox(listings_32148)
```

```{r}
#downtown listings with the class description
test_class_listings = st_join(listings_32148, zones_32148["CLASS_DESC"])
downtown_listings <- subset(test_class_listings, test_class_listings$CLASS_DESC == "Downtown")
``` 

```{r}
nrow(downtown_listings)
```

```{r}
class(downtown_listings)
```

```{r}
tmap_mode("view")
tm_shape(downtown_listings) +
  tm_dots()
```


## Get the attraction

```{r}
cpn <- readOGR(dsn = 'data/spatial',
               layer = 'Common_Place_Names_CPN')
```

```{r}
cpn@data
```

```{r}
filter(cpn@data, CPN_PLACEN == "THE SEATTLE AQUARIUM")
```

### Check if the locations given by Chloe are in the CPN data
```{r}
attraction_loc <- c("PIKE PLACE MARKET","BENAROYA CONCERT HALL","COLUMBIA CENTER","SEATTLE ART MUSEUM","OLYMPIC SCULPTURE PARK","SEATTLE PUBLIC LIBRARY (DOWNTOWN)","SEATTLE GREAT WHEEL","WASHINGTON STATE FERRIES","THE SEATTLE AQUARIUM","KLONDIKE GOLDRUSH")
filter(cpn@data, CPN_PLACEN %in% attraction_loc)
```
*Verdict: yes, it is inside*


```{r}
attractions <- subset(cpn,CPN_PLACEN %in% attraction_loc)
```

```{r}
tm_shape(attractions) +
  tm_dots()
```

```{r}
attraction_names <- attractions$CPN_PLACEN
```

```{r}
class(attraction_names)
```


```{r}
attraction_names <- attraction_names[attraction_names %in% c("OLYMPIC SCULPTURE PARK","KLONDIKE GOLDRUSH","WASHINGTON STATE FERRIES")]
```

```{r}
attraction_names
```


```{r}
attraction_names <- as.character(attraction_names)
```

```{r}
class(attraction_names)
```

#Replacement of location names Benaroya Concert Hall to BENAROYA HALL and Seattle Public Library to CENTRAL LIBRARY
```{r}
attraction_names <- ifelse(attraction_names == "OLYMPIC SCULPTURE PARK","Washington State Convention Center",ifelse(attraction_names == "KLONDIKE GOLDRUSH","KLONDIKE GOLD RUSH NATIONAL HISTORICAL PARK SEATTLE","SPACE NEEDLE"))
```

```{r}
attraction_names
```

```{r}
class(attraction_names)
```


```{r}
attraction_names_geocode <- geocode_OSM(attraction_names)
coordinates(attraction_names_geocode) <- ~lon+lat
```

```{r}
attraction_names_geocode
```

```{r}
tm_shape(attraction_names_geocode) + 
  tm_dots()
```


```{r}
filter_for_correct <- c("PIKE PLACE MARKET","BENAROYA CONCERT HALL","COLUMBIA CENTER","SEATTLE ART MUSEUM","SEATTLE PUBLIC LIBRARY (DOWNTOWN)","SEATTLE GREAT WHEEL","WASHINGTON STATE FERRIES","THE SEATTLE AQUARIUM")
```


```{r}
attractions <- subset(attractions, CPN_PLACEN %in% filter_for_correct)

coordinatesA <- coordinates(attractions)

namesA <- attractions$CPN_PLACEN

coordinatesA
namesA
```

```{r}
coordinatesB <- coordinates(attraction_names_geocode)

namesB <- attraction_names_geocode$query

coordinatesB
namesB
```

```{r}
class(namesA)
class(namesB)
```

```{r}
namesA <- as.character(namesA)
```


```{r}
namesA <- as.data.frame(namesA)
names(namesA) <- "Name"
namesB <- as.data.frame(namesB)
names(namesB) <- "Name"

```


```{r}
namesA
```

```{r}
namesB
```



```{r}
NewAttractions <-  rbind(namesA,namesB)
```

```{r}
NewAttractions
```

```{r}
NewCoordinates <- rbind(coordinatesA, coordinatesB)
NewCoordinates <- as.data.frame(NewCoordinates)
NewCoordinates
```

```{r}
class(NewAttractions)
```

```{r}
class(NewCoordinates)
```


```{r}
attractions2 <- SpatialPointsDataFrame(coords = NewCoordinates,
                                       data = NewAttractions,
                                       proj4string = CRS("+init=epsg:4326"))
```

```{r}
attractions2@data
```


```{r}
attractions2[10,]
```

```{r}
class(downtown_listings)
```

```{r}
downtown_listings <- as(downtown_listings, "Spatial")
```

```{r}
class(downtown_listings)
```


```{r}
attraction_loc12 <- 1:1148
i=1
```


```{r}

i = i

for (airbnb_locs in i:1148) {
     attraction_loc12[i] <- as.vector(osrmRoute(src = downtown_listings[airbnb_locs,], dst = attractions2[10,], sp = TRUE, overview = FALSE))[2]
    
     i = i + 1
     
  }

i  

```

```{r}
attraction_loc12
```

```{r}
distance_matrix <- read_csv('distance_matrix_bygrouping(km).csv')
```

```{r}
distance_matrix
```

```{r}
WashingtonStateConventionCentre <- attraction_loc12
```

```{r}
WashingtonStateConventionCentre
```


```{r}
distance_matrix <- cbind(distance_matrix,WashingtonStateConventionCentre)
```

```{r}
distance_matrix
```

```{r}
distance_matrix$WashingtonStateConventionCentre <- distance_matrix$WashingtonStateConventionCentre*1000
distance_matrix
```

```{r}
write.csv(distance_matrix,'distance_matrix_bygrouping_wConvention(km).csv',row.names = FALSE)
```

```{r}
tm_shape(attractions2) +tm_dots()
```

